\documentclass[a4paper,9pt]{article} % Reduced font size from 10pt to 9pt
% \usepackage{hyperref}
\usepackage[hidelinks]{hyperref}
\usepackage{geometry}
\usepackage{enumitem}
\usepackage{titlesec}
\pagenumbering{gobble}

\geometry{top=0.5in, bottom=0.5in, left=0.5in, right=0.5in} % Adjusted margins to fit everything on one page
\setlength{\parindent}{0pt}

% Custom formatting to center section titles
\titleformat{\section}
  {\normalfont\normalsize\bfseries\filcenter} % Reduced font size of section titles
  {} % No section number
  {0pt} % No spacing between section title and text
  {}

\begin{document}

\begin{center}
    {\LARGE \textbf{Amit Choubey}} \\
    London, UK  DA1 • \href{mailto:amit.katyayana@gmail.com}{amit.katyayana@gmail.com} • 779-665-6823 • \href{https://github.com/amit-chaubey}{GitHub} • \href{ https://huggingface.co/sweatSmile}{HuggingFace}
\end{center}

\vspace{0.1cm} % Reduced vertical space here

\section*{Education}

\textbf{UNIVERSITY OF LIVERPOOL} \hfill Liverpool, UK \\
\textit{MSc. in Data Science \& AI}, Distinction \hfill September 2024 \\
Relevant Coursework: Python Programming, Maths \& Statistics, Database \& Information System, Research Methods, Applied AI, Computational Intelligence, Data Mining \& Visualisation, ML \& Bio-Inspired Optimisation.\\

\vspace{0.1cm} % Reduced vertical space here

\textbf{SRM INSTITUTE OF SCIENCE \& TECHNOLOGY} \hfill Chennai, IND \\
\textit{B.Tech in Electronics \& Instrumentation Engineering}, First-Class Honours \hfill June 2014 \\
Relevant Coursework:  Mathematics III, Neural Networks, Matlab, Modern Control System, DSP. \\
Final Year Project Appreciation by NIEPMD \& HAL.

\section*{Technical Skills \& Projects}

\textbf{Programming}: Python, Flask, Django, SQL, MongoDB, JavaScript, Node.js, Git-Action, CI/CD Pipeline.\\
\textbf{Markup-language}: HTML, Overleaf, Latex.\\
\textbf{Data-Science}: Matplotlib, Seaborn, Pandas, Numpy, Power BI, Tableau, NLP, Open Source LLm, Hugging-Face.\\ 
\textbf{Framework}: Scikit-learn, Pytorch, Keras, Tensor-flow, RAG, LangChain, LlamaIndex, OpenAI API, GGplot.\\
\textbf{Cloud}: AWS S3, EC2, Sagemaker, RedShift, DynamoDB, Database, Billing.\\
\textbf{General Purpose}: MS Excel, MS365, MS Power BI, Prompt, Slack, Web Scrape, Gradio, Streamlit, SPSS.\\
\textbf{Additional}: System Design, ML-System Design, Data Engineering, Kubernetes, Medical-Coding, Graph-Rag using Neo4j.
\vspace{0.2cm}

\textbf{COMP702 MSc Dissertation} \\
Developed a Long-Form Q\&A NLP tool for the finance domain using a Retrieval-Generation Pipeline (RAG). Conducted experiments with 4 retriever models and 6 open-source generative models to determine the optimal combination, and currently presenting findings in a research paper.

\vspace{0.1cm}

\textbf{EI0444 B.Tech Project-Work} \\
Developed a Voice-Controlled Smart Environment system to assist individuals with mobility challenges as part of my final year project (Speech Recognition). 

\section*{Relevant Experience}

\vspace{0.1cm}

\textbf{FREELANCE} \hfill Bengaluru, IND \\
\textit{GenAI Engineer} \hfill December 2022 - July 2023
\begin{itemize}[left=0pt, itemsep=0pt]
\item Spearheaded the design of personalized learning tools for SEND children, including spelling and vocabulary apps powered by advanced LLMs, optimizing educational content delivery and fostering targeted learning outcomes tailored to individual needs.

\end{itemize}

\vspace{0.1cm}

\textbf{BYJU'S} \hfill Bengaluru, IND \\
\textit{ML Engineer -  Learning \& Personalisation} \hfill February 2022 – December 2022
\begin{itemize}[left=0pt, itemsep=0pt]
    \item Designed AI-driven tools for content classification, feedback, and academic tracking, enhancing platforms like AssesEd.
    \item Built knowledge graphs, concept maps, and ML workflows for JEE, NEET, and K-10, improving content optimization.
\end{itemize}

\section*{Leadership \& Teaching}

\begin{itemize}[left=0pt, itemsep=0pt] \item Marketing Campaign Lead: Boosted CORNER HOUSE membership by 20 \% through a targeted marketing initiative. \item Event Organizer: Managed EIEIA-13 Fest logistics, increasing student participation and sponsorship. \item Physics Faculty (Allen Career Institute): Taught 5,000+ students over 6 years using data-driven methods, established new centres, and enhanced student enrolment. \item Volunteer Educator-Part time (UK): Taught Physics and Maths in Liverpool \& London as part of a social giveback, supporting under-represented \& SEND students with tailored lessons. \end{itemize}




\section*{Certifications }


\begin{itemize}[left=0pt, itemsep=0pt]
    \item AWS Certified AI Practitioner (AIF-C01)
    \item AWS Certified Cloud Practitioner (CLF-C02)
    \item UoL Health Tech Hackathon
\end{itemize}

\end{document}